---
title: "EVALUATING EXCLUDING FOOD AND ENERGY CORE INFLATION MEASURES"
author: "Yiyi"
date: "`r Sys.Date()`"
output:
  pdf_document:
  header-includes:
  - \usepackage{placeins}
  - \usepackage{multirow}
  - \usepackage{multicolumn}
  - \usepackage{caption}
  - \usepackage[absolute,overlay]{textpos}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \usepackage{booktabs}
  html_document:
    toc: yes
    df_print: paged
  word_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r rm, include=FALSE}
 rm(list = ls())
Sys.setlocale("LC_TIME", "English")
```

```{r Library, include=FALSE}
#Packages
library(readxl)
library(data.table)
library(lubridate)#extract cpi time to newdata(furniture48)
library(dplyr) 
library(tidyverse) 
library(broom)
library(stargazer)
library(knitr)
library(officer)
library(flextable)
library(magrittr)
library(dplyr)
library(moments)
library(Inflation)
library(ggplot2)
library(zoo)
library(xts)
library(hydroTSM)
library(openair)
library(tibble)
library(miscTools)
library(priceR)
library(Metrics)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(kableExtra)

```

```{r language,message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
Sys.setlocale("LC_TIME","English")
```

# Criteria for evaluation : forecasting future inflation

This work uses Cogley's model to test the forecasting ability of core inflation rate, and compares the forecasting ability of excluding food and energy core inflation rates. Cogley's model is based on Bryan and Cecchetti's definition of core inflation: "Core inflation is changes in the price level that are expected to persist over a long period of time."

According to Bryan and Cecchetti's definition, a valid core inflation is one that is "pure" after removing temporary factors from measured real inflation. On this basis, Cogley developed the following model to evaluate the predictive power of core inflation:

```{r latex, include=FALSE}
#想在r markdown里输入latex公式居中 首先需要首位$$\begin{} \end{}$$
#html公式后面是没有标号的，pdf有
#这个 公式模型 我自己用ols也能做啊？
#就做一个df，有三列数据，第一列x_t+12,第二列x_t,第三列core
#日期的问题
#
```


$$\pi_{t+h}-\pi_{t}=\alpha_{h}+\beta_{h}\left(\pi_{t}-\pi_{t}^{c}\right)+u_{t+h}$$

Here, x represents the headline inflation rate and core x represents some core inflation indicator, both year-on-year data. Parameter h is 6,9 and 12 (month) ahead in this case. For sufficiently large H, the core deviation, $\left(\pi_{t}-\pi_{t}^{c}\right)$, should be inversely related to subsequent changes in inflation, $\pi_{t+h}-\pi_{t}$. Moreover, in order for the candidate to satisfy equation (1), the coefficients in the regression, should satisfy $\alpha=0$ and $\beta = -1$.

Of importance to the forecasting model is the estimated coefficient of $\beta$, which indicates whether core inflation has sufficiently purified the transitory component. Because if the absolute value of the estimated coefficient is equal to 1, it indicates that the model is a random walk process, and the components removed from the core inflation do not contain any information that predicts future overall inflation. If $\beta=-1$, the forecasting capacity for core inflation is the best . This proves that core inflation has fully captured the trend components of overall inflation and has a complete forecasting ability for future inflation.

1.  If the $|\beta|<1$, it indicates that subsequent changes in inflation are overestimated;

2.  If the $|\beta|>1$, it shows that underestimation of the current temporary movement in headline inflation.

Therefore, the closer the absolute value of the estimated regression coefficient $\beta$ is to 1, the better the predictive power of core inflation is. In addition, the root mean square error RMSE $=\sqrt{\frac{1}{\mathrm{~T}} \sum_{\mathrm{t}=1}^{\mathrm{T}}\left(\pi_{\mathrm{t}}-\hat\pi_{\mathrm{t}}\right)^{2}}$obtained by Cogley regression represents the deviation between the predicted value and the actual value. $\hat\pi_{\mathrm{t}}$ is the forecast value of the inflation rate. The smaller the RMSE, the more accurate the forecast. and the better the forecast of core inflation.

```{r V1 excluding, include=FALSE}
#首先导入数据
#05.1对应的是x+12是06.1
#那尾部又不够了， 重新搞一份全的cpi重新提取把
core_headline<-read_excel("V2 core excluding food and energy.xlsx","Comparision")
#读取全部的cpi数据
headline_df<-read_excel("UK ALL year CPI.xls")
#提取2006JAN -2020 DEC的数据作为x+12
#开始结束的位置
start_poisition<-which(headline_df$Title=="2006 JAN")
end_poisition<-which(headline_df$Title=="2020 DEC")
#把开始结束的之间的内容提取到主df里
core_headline[,7]<-headline_df[start_poisition:end_poisition,2]
#命名新的列
colnames(core_headline)[7]<-c("x+12")
#把几个数据都改为numerical
core_headline[, 4:7] <- sapply(core_headline[,4:7], as.numeric)
core_headline<-data.frame(core_headline)
#生成x_core-x -> difference
core_headline$difference<- core_headline$CPI.ANNUAL.RATE.00..ALL.ITEMS.2015.100 - core_headline$Core.inflation.excluding.food.and.energy.
#left difference
colnames(core_headline)<-c("titlle","time","origin","core","CPI","approx","x+12","difference")
core_headline$left_difference<-core_headline$`x+12`- core_headline$CPI
#core_jeadline$difference 改名字为beta方便输出
colnames(core_headline)[8]<-c("beta")
#regression
regression<-lm(core_headline$left_difference~ beta,data = core_headline)

```

```{r 6 12 food,include=FALSE}
#6 months ahead
start_poisition_6<-which(headline_df$Title=="2005 JUL")
end_poisition_6<-which(headline_df$Title=="2020 JUN")
#把开始结束的之间的内容提取到主df里
core_headline$"6 month ahead"<-headline_df[start_poisition_6:end_poisition_6,2]
#9 months 
start_poisition_9<-which(headline_df$Title=="2005 OCT")
end_poisition_9<-which(headline_df$Title=="2020 SEP")
#把开始结束的之间的内容提取到主df里
core_headline$"9 month ahead"<-headline_df[start_poisition_9:end_poisition_9,2]
core_headline[, 10:11] <- sapply(unlist(core_headline[,10:11]), as.numeric)
#6 month diff
core_headline$"6 months diff"<-core_headline$`6 month ahead`-core_headline$CPI
#9month diff
core_headline$"9 months diff"<-core_headline$`9 month ahead`- core_headline$CPI
#regression 6 head
regression_6<-lm(core_headline$`6 months diff`~ beta,data = core_headline)
#regression 9 head
regression_9<-lm(core_headline$`9 months diff`~ beta,data = core_headline)
```

#Trimmed Mean

```{r first try trimmed, include=FALSE}
#Trend
#我把trend的也向前做了12期，其实是错误的
#我唯一要做的就是ukcpi向前推12期
#如果我想做05.1-19.12的， 那对应的数据范围是05.2-20.12
#尝试建立连续12个月的预测
#%%
#95.1-21.10
TM<-read_excel("Trimmed mean.xlsx")
TM<-as.data.table(TM)
#我的idea是：
#1.首先生成12列lead，每一行第一个数都是上一列的第二行
#2. 这样后面十二列都减去第一列就是x12— x。也就是等式左边的数据了
#lead 超前12个月的预测
TM <- TM[, unlist(lapply(.SD, shift,type = "lead", n = 0:12), recursive = FALSE),.SDcol=2]
#
TM<-data.frame(TM)
#这个式子不在data。frame里运行不了。
TM[2:ncol(TM)] <- TM[2:ncol(TM)]-TM[,1]
#这代码的意思是： 对2：13列的数据减去他们自己的lag1数据
#sad<-TM %>% mutate(across(2:13, ~. - lag(.)) )
#date
date_t = seq(from = as.Date("1995-01-01"), to = as.Date("2021-10-01"),
           by = "month")#生成日期
TM<-add_column(TM,date_t,.before = 1)
#挑选05.1 ： 19.12
TM_05<-TM[TM$date_t>="2005-01-01" & TM$date_t<="2019-12-01",]


```


```{r all time forcast main code,include=FALSE}

#读取cpi 数据
#1989 JAn 开始
#2021 OCT 结束
start_poisition_all<-which(headline_df$Title=="1989 JAN")
end_poisition_all<-which(headline_df$Title=="2021 OCT")
CPI_alll<-headline_df[start_poisition_all:end_poisition_all,2]
#转化数据类型
CPI_alll[,1]<-as.numeric(unlist(CPI_alll[,1]))
#
CPI_alll<-as.data.table(CPI_alll)
#lead 超前12个月的预测
CPI_alll <- CPI_alll[, unlist(lapply(.SD, shift,type = "lead", n = 0:12), recursive = FALSE),.SDcol=1]
#
CPI_alll<-data.frame(CPI_alll)
#这个式子不在data。frame里运行不了。
#2:13列 x+1 - x+12 都 减去 x
CPI_alll[2:ncol(CPI_alll)] <- CPI_alll[2:ncol(CPI_alll)]-CPI_alll[,1]
#建立时间序列
#date
date_all = seq(from = as.Date("1989-01-01"), to = as.Date("2021-10-01"),
           by = "month")#生成日期
CPI_alll<-add_column(CPI_alll,date_all,.before = 1)
#我需要05.1-19.12
CPI519<-CPI_alll[CPI_alll$date_all>="2005-01-01" & CPI_alll$date_all<="2019-12-01",]
#列命名
# 1.2.3.... months diff?
#
colnames(CPI519)[2]<-c("CPI")
colnames(CPI519)[3:14]<- paste(1:12,"months difference ",sep=" ")
#把05-19的各种core 导入cpi519 并且 core difference with CPI
 #excluding food and energy
CPI519$excluding_food_and_energy<-CPI519$CPI - core_headline$core
#trimmed
CPI519$Trimmed_mean<-CPI519$CPI -TM_05$CPI.trim..5..1
#regression
#每个core 对应12列
# #excluding food and energy
res_excluding<-lapply(3:14, function(x) lm(CPI519[,x]~ CPI519$excluding_food_and_energy))
RMSE_food<-unlist(lapply(1:12, function(x) sqrt(mean(res_excluding[[x]]$residuals^2)))
)
cof_food_alpha<-unlist(lapply(1:12, function(x) res_excluding[[x]]$coefficients[1]))
cof_food_beta<-unlist(lapply(1:12, function(x) res_excluding[[x]]$coefficients[2]))

#Trimmed mean
res_trimmed<-lapply(3:14, function(x) lm(CPI519[,x]~ CPI519$Trimmed_mean))
RMSE_trimmed<-unlist(lapply(1:12, function(x) sqrt(mean(res_trimmed[[x]]$residuals^2)))
)
cof_trimmed_alpha<-unlist(lapply(1:12, function(x) res_trimmed[[x]]$coefficients[1]))
cof_trimmed_beta<-unlist(lapply(1:12, function(x) res_trimmed[[x]]$coefficients[2]))

#
dt<-cbind(RMSE_food,cof_food_alpha,cof_food_beta)
rownames(dt)<-paste(1:12,"months ahead")
colnames(dt)<-c("RMSE","$\\alpha$","$\\beta$" )
dt %>%
  kbl() %>%
  kable_paper("hover", full_width = F)

```

```{r output, echo=FALSE}
together<-cbind(RMSE_food,cof_food_alpha,cof_food_beta,RMSE_trimmed,cof_trimmed_alpha,cof_trimmed_beta)
rownames(together)<-paste(1:12,"months ahead")
colnames(together)<-c("RMSE","$\\alpha$","$\\beta$","RMSE","$\\alpha$","$\\beta$" )

kbl(together) %>%
  kable_classic() %>%
  add_header_above(c(" " , "Excluding Food and Energy" = 3, "Trimmed Mean" = 3)) %>%
  add_header_above(c(" ", "Core Inflation 6" = 6))


```


# Results

From the above discussion, I used my own data to re-simulate the values of the parameters.The results please see Table 1.

## RMSE



```{r eval=FALSE, include=FALSE}
### 6 months ahead
#RMSE 6
RSS <- c(crossprod(regression_6$residuals))
MSE <- RSS / length(regression_6$residuals)
sig2 <- RSS / regression_6$df.residual

sqrt(mean(regression_6$residuals^2))


### 9 months ahead

#RMSE 9
RSS <- c(crossprod(regression_9$residuals))
MSE <- RSS / length(regression_9$residuals)
sig2 <- RSS / regression_9$df.residual

sqrt(mean(regression_9$residuals^2))


### 12 months ahead


#RMSE 12
RSS <- c(crossprod(regression$residuals))
MSE <- RSS / length(regression$residuals)
sig2 <- RSS / regression$df.residual

sqrt(mean(regression$residuals^2))


## Coefficients

### 6 months ahead

summary(regression_6)

### 9 months ahead

summary(regression_9)


### 12 months ahead

summary(regression)
```

```{=tex}
\begin{table}[h]
\centering
\caption{Forecasting future inflation}
\label{tab:my-table}
\begin{tabular}{|c|cll|}
\hline
H                       & \multicolumn{3}{c|}{Excluding Food and Energy}                                               \\ \hline
                        & \multicolumn{1}{c|}{a}       & \multicolumn{1}{c|}{b}        & \multicolumn{1}{c|}{RMSE}     \\ \hline
\multicolumn{1}{|l|}{6} & \multicolumn{1}{l|}{0.12189} & \multicolumn{1}{l|}{-0.38370} & 0.879791                      \\ \hline
\multicolumn{1}{|l|}{9} & \multicolumn{1}{l|}{0.17481} & \multicolumn{1}{l|}{-0.60511} & 1.053181                      \\ \hline
12                      & \multicolumn{1}{c|}{0.229}   & \multicolumn{1}{c|}{-0.81695} & \multicolumn{1}{c|}{1.155487} \\ \hline
\end{tabular}
\end{table}
```
# Conclusions

As expected, all Cogley regressions of the core inflation rate with $\beta$ estimates are all negative. The beta keeps falling as the number of forecast periods rises; The forecast RMSE for core inflation rates increases as the number of forecast periods increases continuously. This suggests that the longer the forecast period, the more inaccurate the forecast.
