---
title: "AIC stepwise"
author: "Yiyi"
date: "`r Sys.Date()`"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
 rm(list = ls())
Sys.setlocale("LC_TIME", "English")
```
## Packages
```{r Library, include=FALSE}
library(readxl)
library(data.table)
library(lubridate)#extract cpi time to newdata(furniture48)
library(dplyr) 
library(tidyverse) 
library(broom)
library(stargazer)
library(knitr)
library(officer)
library(flextable)
library(magrittr)
library(dplyr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
Sys.setlocale("LC_TIME","English")

cpi <- read_excel("cpi data/cpi+division+group.xlsx")


setDF(cpi)#convert to 'data.frame'

#
cols.num <- c(colnames(cpi))
cpi[cols.num] <- sapply(cpi[cols.num],as.numeric)
#sapply(cpi,class)

cpi <- as.data.table(cpi)
colnames(cpi) = gsub("&", "and", colnames(cpi))

COPY<-copy(cpi)
col_name<-colnames(COPY)
colnames(COPY)[!complete.cases(t(COPY))][1]#显示有na的部门,列
na_col<-vector()
for (i in 1:length(colnames(COPY)[!complete.cases(t(COPY))])) {
   na_col[i]<- ((which(colnames(COPY)==colnames(COPY)[!complete.cases(t(COPY))][i])))
}
```
**新的CoPy是包含cpi的**
## na_col有na的列名的位置

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

na_col<-na_col[1:(length(na_col)-2)]
length(na_col)
```


```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
not_any_na <- function(x) all(!is.na(x))#把年限不够缺失的部门删掉
COPY<-COPY %>% select(where(not_any_na))
cpi<-COPY

```


```{r}
tracemem(COPY)==tracemem(cpi)


Data_A = as.data.table (cpi)
#



#
Varnames <- copy(names(Data_A))
Data_A[, (names(Data_A)) := lapply(.SD, as.numeric)][,
                                                     rn := .I]
melted <- melt(Data_A, id.vars="rn")[,
                                     (paste0("lag_", 0:12)) := shift(value, 0:12, type="lag"),
                                     by=variable][, 
                                                  value:=NULL][]
res <- dcast.data.table(melt(melted, id.vars=c("rn", "variable"), variable.name="lag"),
                        rn ~ variable + lag, sum)

#view results
res[, ncol(res), with=FALSE]
# lagged variable generation ----------------------------------------------


cpi <- cpi[, unlist(lapply(.SD, shift, n = 0:12), recursive = FALSE)]#lags generation


# Monthly Dummies ---------------------------------------------------------


cpi$time <- seq.Date(from = as.Date("1988/01/01",format = "%Y/%m/%d"), by = "month", length.out = 387)
cpi$time <- format(cpi$time, format = "%b")
Sys.setlocale("LC_TIME","English")
cpi <- fastDummies::dummy_cols(cpi, select_columns = "time", remove_most_frequent_dummy = TRUE,
)
cpi$time1 <- seq.Date(from = as.Date("1988/01/01",format = "%Y/%m/%d"), by = "month", length.out = 387)
#



# Extract time from 1993-2019 ---------------------------------------------



newdata <- with(cpi, cpi[(time1) >= "1993-01-01" & (time1) <= "2019-12-01", ])#start from 93.1
Trend <- seq_along(newdata$time1)
#sapply(newdata, class)



# deal with copy ----------------------------------------------------------


COPY$time1 <- seq.Date(from = as.Date("1988/01/01",format = "%Y/%m/%d"), by = "month", length.out = 387)
COPY <- with(COPY, COPY[(time1) >= "1993-01-01" & (time1) <= "2019-12-01", ])
COPY = subset(COPY, select = -c(time1) )
#lag
```

lag 是2:13 代表1:12. newdata里的1代表的是原数据.
首先把2:13 存储起来, 用paste0(2:13,加上"$")用来匹配以2:13数字结尾的列? 







## Lag and VAT
```{r}
old13<-c(2:13)
for (i in 1:12) {

  assign(paste0("lag",i),select(newdata,ends_with(paste0(old13[i]))))

}
lag1 <- lag1 %>% select(-contains("12"))
lag2 <- lag2 %>% select(-contains("13"))
VAT1 <- as.numeric(newdata$`time1` == "2008-12-01")
VAT2 <- as.numeric(newdata$`time1` == "2010-01-01")
VAT3 <- as.numeric(newdata$`time1` == "2011-01-01")
Recession <- as.numeric(newdata$`time1` >= "2008-04-01" & newdata$`time1`<= "2009-06-01")
```
## Monthly dummies variable position

```{r  MONTYHLY DUMMIES }
monthname<-c("time_Apr","time_Aug", "time_Dec",  "time_Jan","time_Jul","time_Jun" ,"time_Mar","time_May","time_Nov","time_Oct","time_Sep")
month_dummies_position<-vector()
for (i in 1:length(monthname)) {
  month_dummies_position[i]<-
 which(colnames(newdata)==monthname[i])

}
```

## Create time_Apr etc.
the correct version. 首先把月度虚拟变量存储到cpilag 里. 然后用同一迭代变量 送到各自的time_下.
**注意, 双迭代变量还未完全掌握, i 和j 一起用 必出错**
```{r   }
monthdummies<-newdata[,..monthname]
#monthdummies<-newdata[,1991:2y001]

  for (i in 1:11) {
  assign(colnames(monthdummies)[i],as.numeric(unlist(monthdummies[[i]]))  )
  }


```
## CPI LDV variables position

```{r simply lag and cpi}

lag.list <- mget(paste0("lag", 1:12))


for (i in 1:12) {
  assign(paste0("lag",i),as.data.frame(lag.list[[i]]))
}

COPY <- as.data.frame(COPY)



# CPI-LAGS ----------------------------------------------------------------
cpi.list<-c(paste0("CPI ALL ITEMS",2:13))

for (i in 1:length(cpi.list)) {
  print(which(colnames(newdata)==cpi.list[i]))
  
}   
cpilag<-newdata[,2:13]
for (i in 1:12) {

    
 
  assign(paste0("CPI_lag",i),as.numeric(unlist(cpilag[,..i])))
  
}


```

## Rgression

```{r model}
# Regression Equation -----------------------------------------------------


reg.model <- lapply(1:length(COPY), function(x) lm(COPY[,x] ~ lag1[,x]+lag2[,x]+lag3[,x]+lag4[,x]+
                                            lag5[,x]+lag6[,x]+lag7[,x]+lag8[,x]+lag9[,x]+
                                            lag10[,x]+lag11[,x]+lag12[,x]+ time_Aug + 
                                            time_Dec+ time_Apr+ time_Jan+time_Jul+time_Jun +
                                            time_Mar+time_May+time_Nov+time_Oct+time_Sep+VAT1+VAT2+VAT3+Recession+Trend)
)

for (i in 1:length(COPY)) {
  names(reg.model[[i]]$coefficients)<-c('Constant','lag1','lag2',"lag3","lag4","lag5","lag6","lag7","lag8","lag9","lag10","lag11","lag12",
                                        "time_Aug" , 
                                        "time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Mar",
                                        "time_May","time_Nov","time_Oct","time_Sep","VAT1","VAT2","VAT3","Recession","Trend")
}

regression <- lapply(1:length(COPY), function(x) lm(COPY[,x] ~ lag1[,x]+lag2[,x]+lag3[,x]+lag4[,x]+lag5[,x]+lag6[,x]+lag7[,x]+
                                             lag8[,x]+lag9[,x]+lag10[,x]+lag11[,x]+lag12[,x]+CPI_lag1+CPI_lag2+CPI_lag3+CPI_lag4+CPI_lag5+CPI_lag6+CPI_lag7+
                                             CPI_lag8+CPI_lag9+
                                             CPI_lag10+CPI_lag11+CPI_lag12+ time_Aug + 
                                             time_Dec+ time_Apr+ time_Jan+time_Jul+time_Jun +time_Mar+
                                             time_May+time_Nov+time_Oct+time_Sep+VAT1+VAT2+VAT3+Recession+Trend)
)
for (i in 1:length(COPY)) {
  names(regression[[i]]$coefficients)<-c('Constant','lag1','lag2',"lag3","lag4","lag5","lag6","lag7","lag8","lag9","lag10","lag11","lag12",
                                         "CPI_lag1","CPI_lag2","CPI_lag3","CPI_lag4","CPI_lag5","CPI_lag6","CPI_lag7","CPI_lag8","CPI_lag9",
                                         "CPI_lag10","CPI_lag11","CPI_lag12","time_Aug" , 
                                         "time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Mar",
                                         "time_May","time_Nov","time_Oct","time_Sep","VAT1","VAT2","VAT3","Recession","Trend")
}


```

## backward 过程.
```{r}


percent <- function(x, digits = 2, format = "f", ...) {
  paste0(formatC(100 * x, format = format, digits = digits, ...), "%")
}
# Weight ------------------------------------------------------------------
weight<- list(0.109,	0.042,	0.063,	0.115,	0.067,	0.022,	0.152,	0.023,	0.152,	0.019,	0.137,	0.099
              
)
Reduce("+",weight)
```


**backward == slr.total**
```{r}
backward<-list()
for (i in 1: length(regression)) {
    backward[[i]] <- step(regression[[i]], direction='backward', scope=formula(regression[[i]]), trace=0)
}
```

## 18个漏网之鱼的, 因为部分数据不全 单独出列

```{r}
b.18<-list()
for (i in 1: length(na_col)) {
    b.18[[i]] <- step(regression[[na_col[i]]], direction='backward', scope=formula(regression[[na_col[i]]]), trace=0)
}
```


## 替换backward变量名称
```{r}

backward[sapply(backward, is.null)] <- NULL

#替换名称
search_for_these <- c("lag1[, x]","lag2[, x]","lag3[, x]","lag4[, x]","lag5[, x]","lag6[, x]","lag7[, x]","lag8[, x]","lag9[, x]","lag10[, x]","lag11[, x]","lag12[, x]")
 replace_with_these <- c("lag1","lag2","lag3","lag4","lag5","lag6","lag7","lag8","lag9","lag10","lag11","lag12")
 found<-list()
for (i in 1:length(backward)) {
  found[[i]] <- match(names(backward[[i]]$coefficients), search_for_these, nomatch = 0)
  names(backward[[i]]$coefficients)[names(backward[[i]]$coefficients) %in% search_for_these] <- replace_with_these[found[[i]]]
}
```

## 替换b18变量名称
```{r}
b.18[sapply(b.18, is.null)] <- NULL

#替换名称
search_for_these <- c("lag1[, x]","lag2[, x]","lag3[, x]","lag4[, x]","lag5[, x]","lag6[, x]","lag7[, x]","lag8[, x]","lag9[, x]","lag10[, x]","lag11[, x]","lag12[, x]")
 replace_with_these <- c("lag1","lag2","lag3","lag4","lag5","lag6","lag7","lag8","lag9","lag10","lag11","lag12")
 found<-list()
for (i in 1:length(b.18)) {
  found[[i]] <- match(names(b.18[[i]]$coefficients), search_for_these, nomatch = 0)
  names(b.18[[i]]$coefficients)[names(b.18[[i]]$coefficients) %in% search_for_these] <- replace_with_these[found[[i]]]
}
```


**=41最多一共41个变量**


哈哈哈哈找到怎么删除p值小于0.05的coefficients
```{r}
names(which((summary(regression[[2]])$coeff[-1,4] > 0.01)==TRUE))
```



## 不显著的名字
```{r}
typec<-list()
for(i in 1:length(backward)){
  typec[[i]]<-names(which(((summary(backward[[i]])$coeff[-1,4])>0.01)==TRUE))
}
typec[1]

```

## 剔除不显著变量名字, 保留显著变量
```{r}
for(i in 1:length(backward)){
  backward[[i]]$coefficients <- backward[[i]]$coefficients[!names(backward[[i]]$coefficients) %in% typec[[i]] ]


}

for(i in 1:length(b.18)){
  b.18[[i]]$coefficients <- b.18[[i]]$coefficients[!names(b.18[[i]]$coefficients) %in% typec[[i]] ]


}
```
# 各部门汇报 
### 01 Food and non-alcoholic beverages

2-15
```{r}

tab_model(backward[2:7],
          rm.terms=c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Apr",
                   "time_Mar","time_May","time_Nov","time_Oct","time_Sep", "VAT1","VAT2",
                   "VAT3","Recession","Trend",'Constant',"(Intercept)"), 
            show.ci = FALSE, 
  show.p = FALSE,
string.est = "",
  p.style = "stars",
  CSS = css_theme("cells"),
  dv.labels= c(colnames(COPY[2:7]))
)

```



```{r}
tab_model(backward[8:15],
          rm.terms=c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Apr",
                   "time_Mar","time_May","time_Nov","time_Oct","time_Sep", "VAT1","VAT2",
                   "VAT3","Recession","Trend",'Constant',"(Intercept)"), 
            show.ci = FALSE, 
  show.p = FALSE,
string.est = "",
  p.style = "stars",
  CSS = css_theme("cells"),
  dv.labels= c(colnames(COPY[8:15]))
)

```


### 02 Alcoholic beverages, tobacco and narcotics
16-21
```{r}
tab_model(backward[16:21],
          rm.terms=c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Apr",
                   "time_Mar","time_May","time_Nov","time_Oct","time_Sep", "VAT1","VAT2",
                   "VAT3","Recession","Trend",'Constant',"(Intercept)"), 
            show.ci = FALSE, 
  show.p = FALSE,
string.est = "",
  p.style = "stars",
  CSS = css_theme("cells"),
  dv.labels= c(colnames(COPY[16:21]))
)

```

### 03 Clothing and footwear
22-27
```{r}
tab_model(backward[22:27],
          rm.terms=c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Apr",
                   "time_Mar","time_May","time_Nov","time_Oct","time_Sep", "VAT1","VAT2",
                   "VAT3","Recession","Trend",'Constant',"(Intercept)"), 
            show.ci = FALSE, 
  show.p = FALSE,
string.est = "",
  p.style = "stars",
  CSS = css_theme("cells"),
  dv.labels= c(colnames(col_name[22:27]))
)

```
### 04 Housing, water, electricity, gas and other fuels
28:40
```{r}
tab_model(backward[28:34],
          rm.terms=c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Apr",
                   "time_Mar","time_May","time_Nov","time_Oct","time_Sep", "VAT1","VAT2",
                   "VAT3","Recession","Trend",'Constant',"(Intercept)"), 
            show.ci = FALSE, 
  show.p = FALSE,
string.est = "",
  p.style = "stars",
  CSS = css_theme("cells"),
  dv.labels= c(colnames(col_name[28:34]))
)

```
```{r}
tab_model(backward[35:40],
          rm.terms=c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Apr",
                   "time_Mar","time_May","time_Nov","time_Oct","time_Sep", "VAT1","VAT2",
                   "VAT3","Recession","Trend",'Constant',"(Intercept)"), 
            show.ci = FALSE, 
  show.p = FALSE,
string.est = "",
  p.style = "stars",
  CSS = css_theme("cells"),
  dv.labels= c(colnames(col_name[35:40]))
)

```
### 05 Furnishings, household equipment and routine household maintenance

41:53 41:53-1=52 41:52
48没有
```{r}
tab_model(backward[41:47],
          rm.terms=c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Apr",
                   "time_Mar","time_May","time_Nov","time_Oct","time_Sep", "VAT1","VAT2",
                   "VAT3","Recession","Trend",'Constant',"(Intercept)"), 
            show.ci = FALSE, 
  show.p = FALSE,
string.est = "",
  p.style = "stars",
  CSS = css_theme("cells"),
  dv.labels= c(colnames(col_name[41:47]))
)

```
48
48 49 50 51 52 53 c
[1]48 49 50 51 52 b
```{r}
stargazer(b.18[1],backward[48:52],
          star.char = c("*"),
          star.cutoffs = c(0.01),
          notes = c(" * p<0.01; "),
          omit = c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Mar","time_May","time_Nov","time_Oct","time_Sep",
                   "VAT1","VAT2","VAT3","Recession","Trend",'Constant',"time_Apr"),
          
  dep.var.labels.include = FALSE,
  notes.append = FALSE,
  # order = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20),
  report = "vc*",
  align = TRUE,
  header = FALSE,
  df = FALSE,
  digits = 2, single.row = TRUE,
  model.numbers = FALSE,
  column.labels = c(colnames(col_name[48:53])),
  summary = FALSE,
  out = "F:/R workspace/Modelling-UK-inflation-quarterly-/AIC output/5-2.html",
  omit.stat=c("LL","ser","f"),
  se = NULL, type = "html"
)
```

### 06 Health

54:61 54-1: 61-6 53:55
54 55 56 *57* 58 59 60 *61* c 
53 54 55 *2*  3  4  5  *6*  b 
```{r}
stargazer(backward[53:55],
          star.char = c("*"),
          star.cutoffs = c(0.01),
          notes = c(" * p<0.01; "),
          omit = c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Mar","time_May","time_Nov","time_Oct","time_Sep",
                   "VAT1","VAT2","VAT3","Recession","Trend",'Constant',"time_Apr"),
          
  dep.var.labels.include = FALSE,
  notes.append = FALSE,
  # order = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20),
  report = "vc*",
  align = TRUE,
  header = FALSE,
  df = FALSE,
  digits = 2, single.row = TRUE,
  model.numbers = FALSE,
  column.labels = c(colnames(col_name[54:56])),
  summary = FALSE,
  out = "F:/R workspace/Modelling-UK-inflation-quarterly-/AIC output/6-1.html",
  omit.stat=c("LL","ser","f"),
  se = NULL, type = "html"
)
```


```{r}
stargazer(b.18[2],b.18[3],b.18[4],b.18[5],b.18[6],
          star.char = c("*"),
          star.cutoffs = c(0.01),
          notes = c(" * p<0.01; "),
          omit = c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Mar","time_May","time_Nov","time_Oct","time_Sep",
                   "VAT1","VAT2","VAT3","Recession","Trend",'Constant',"time_Apr"),
          
  dep.var.labels.include = FALSE,
  notes.append = FALSE,
  # order = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20),
  report = "vc*",
  align = TRUE,
  header = FALSE,
  df = FALSE,
  digits = 2, single.row = TRUE,
  model.numbers = FALSE,
  column.labels = c(colnames(col_name[57:61])),
  summary = FALSE,
  out = "F:/R workspace/Modelling-UK-inflation-quarterly-/AIC output/6-2.html",
  omit.stat=c("LL","ser","f"),
  se = NULL, type = "html"
)
```


### 07 Transport

62:76 62-6:76-9 56:67

62 63 64 *65* 66 67 68 c
56 57 58 *7*  59 60 61 b
```{r}
na_col[7]#65

stargazer(backward[56:58],b.18[7],backward[59:61],#1+6=7
          star.char = c("*"),
          star.cutoffs = c(0.01),
          notes = c(" * p<0.01; "),
          omit = c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Mar","time_May","time_Nov","time_Oct","time_Sep",
                   "VAT1","VAT2","VAT3","Recession","Trend",'Constant',"time_Apr"),
          
  dep.var.labels.include = FALSE,
  notes.append = FALSE,
  # order = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20),
  report = "vc*",
  align = TRUE,
  header = FALSE,
  df = FALSE,
  digits = 2, single.row = TRUE,
  model.numbers = FALSE,
  column.labels = c(colnames(col_name[62:68])),
  summary = FALSE,
  out = "F:/R workspace/Modelling-UK-inflation-quarterly-/AIC output/7-1.html",
  omit.stat=c("LL","ser","f"),
  se = NULL, type = "html"
)
```
62 63 64 65 66 67 *8* *9* backward
69 70 71 72 73 74 *75* *76* col_name
```{r}
stargazer(backward[62:67],b.18[8],b.18[9],
          star.char = c("*"),
          star.cutoffs = c(0.01),
          notes = c(" * p<0.01; "),
          omit = c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Mar","time_May","time_Nov","time_Oct","time_Sep",
                   "VAT1","VAT2","VAT3","Recession","Trend",'Constant',"time_Apr"),
          
  dep.var.labels.include = FALSE,
  notes.append = FALSE,
  # order = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20),
  report = "vc*",
  align = TRUE,
  header = FALSE,
  df = FALSE,
  digits = 2, single.row = TRUE,
  model.numbers = FALSE,
  column.labels = c(colnames(col_name[69:76])),
  summary = FALSE,
  out = "F:/R workspace/Modelling-UK-inflation-quarterly-/AIC output/7-2.html",
  omit.stat=c("LL","ser","f"),
  se = NULL, type = "html"
)
```



### 08 Communication

77:79 77-9:79-9 68:70
```{r}
stargazer(backward[68:70],
          star.char = c("*"),
          star.cutoffs = c(0.01),
          notes = c(" * p<0.01; "),
          omit = c("time_Aug","time_Dec", "time_Feb", "time_Jan","time_Jul","time_Jun" ,"time_Mar","time_May","time_Nov","time_Oct","time_Sep",
                   "VAT1","VAT2","VAT3","Recession","Trend",'Constant',"time_Apr"),
          
  dep.var.labels.include = FALSE,
  notes.append = FALSE,
  # order = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20),
  report = "vc*",
  align = TRUE,
  header = FALSE,
  df = FALSE,
  digits = 2, single.row = TRUE,
  model.numbers = FALSE,
  column.labels = c(colnames(col_name[77:79])),
  summary = FALSE,
  out = "F:/R workspace/Modelling-UK-inflation-quarterly-/AIC output/8.html",
  omit.stat=c("LL","ser","f"),
  se = NULL, type = "html"
)
```


### 09 Recreation and culture

[80:101] 80-9:101-15 71:86

### 10 Education

102 102-15=87

### 11 Restaurants and hotels

103：107 103-15:107-16 88:91

### 12 Miscellaneous goods and services

108：122 108-16:122-18 92:104






