---
output: pdf_document
---


# Data
## Import
```{r, echo=TRUE}
data <- read.csv("data.csv")
head(data)
```


## Putting your entire data into the .rmd file
Applying the function `dput()` to an object gives you the code needed to reproduce that object. So you could paste that code into your `.rmd` file if you don't want to have extra data files. This makes sense were data files are small.

```{r}
dput(data)
```

You can then insert the dput output in your `.rmd` as below.

```{r eval=FALSE, include=TRUE}
data <- structure(list(X = 1:50, speed = c(4L, 4L, 7L, 7L, 8L, 9L, 10L, 
10L, 10L, 11L, 11L, 12L, 12L, 12L, 12L, 13L, 13L, 13L, 13L, 14L, 
14L, 14L, 14L, 15L, 15L, 15L, 16L, 16L, 17L, 17L, 17L, 18L, 18L, 
18L, 18L, 19L, 19L, 19L, 20L, 20L, 20L, 20L, 20L, 22L, 23L, 24L, 
24L, 24L, 24L, 25L), dist = c(2L, 10L, 4L, 22L, 16L, 10L, 18L, 
26L, 34L, 17L, 28L, 14L, 20L, 24L, 28L, 26L, 34L, 34L, 46L, 26L, 
36L, 60L, 80L, 20L, 26L, 54L, 32L, 40L, 32L, 40L, 50L, 42L, 56L, 
76L, 84L, 36L, 46L, 68L, 32L, 48L, 52L, 56L, 64L, 66L, 54L, 70L, 
92L, 93L, 120L, 85L)), 
class = "data.frame", row.names = c(NA, 
-50L))
```

# Tables {#sec:tables}
Producing good tables and referencing these tables within a R Markdown PDF has been a hassle but got much better. Examples that you may use are shown below. The way you reference tables is slightly different, e.g., for `stargazer` the label is contained in the function, for `kable` it's contained in the chunk name.

## stargazer(): Summary and regression tables

Table \@ref(tab1) shows summary stats of your data.^[To reference the table where you set the identifier in the stargazer function you only need to use the actual label, i.e., ´tab1´.] I normally use `stargazer()` [@hlavac2013stargazer] which offers extreme flexibility regarding table output (see `?stargazer`). 


```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
stargazer(cars, 
          title = "Summary table with stargazer",
          label="tab1", 
          table.placement = "H", 
          header=FALSE)
```

Table \@ref(tab2) shows the output for a regression table. Make sure you name all your models and explicitly refer to model names (M1, M2 etc.) in the text.

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(stargazer)
model1 <- lm(speed ~ dist, data = cars)
model2 <- lm(speed ~ dist, data = cars)
model3 <- lm(dist ~ speed, data = cars)
stargazer(model1, model2, model3,
          title = "Regression table with stargazer",
          label="tab2", 
          table.placement = "H", 
          column.labels = c("M1", "M2", "M3"),
          model.numbers = FALSE,
          header=FALSE)
```