---
title: "Total Expenditure into monthly data"
author: "Yiyi"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: yes
  header-includes:
  - \usepackage{placeins}
  - \usepackage{multirow}
  - \usepackage{multicolumn}
  - \usepackage{caption}
  - \usepackage[absolute,overlay]{textpos}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \usepackage{booktabs}
  html_document:
    toc: yes
    df_print: paged
  word_document: default

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r rm, include=FALSE}
 rm(list = ls())
Sys.setlocale("LC_TIME", "English")
```

```{r Library, include=FALSE}
#Packages
library(readxl)
library(data.table)
library(lubridate)#extract cpi time to newdata(furniture48)
library(tidyverse) 
library(broom)
library(stargazer)
library(knitr)
library(officer)
library(flextable)
library(magrittr)
library(dplyr)
library(moments)
library(Inflation)
library(ggplot2)
library(zoo)
library(xts)
library(hydroTSM)
library(openair)
library(tibble)
library(miscTools)
library(priceR)
library(Metrics)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(kableExtra)
library(gridExtra)
library(egg)
library(grid)
library(cowplot)
library(spatstat)#shift有重复
library(SciViews)
library(sos)
library(nowcasting)
```

```{r language,message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
Sys.setlocale("LC_TIME","English")
```

```{r , include=FALSE}
DF<-read_excel("consumption data.xlsx")
#分别生成
#jan,april,jul,oct
#96年q4*1/3+97年q1 * 2/3
third<-DF$`0`*1/3
san.fen.zhi.yi<-append(third,0,after = 0)
#
two<-DF$`0`*2/3
san.fen.zhi.2<-append(two,0,after = 99)
#
di.1.yue<-rowMeans(cbind(san.fen.zhi.2, san.fen.zhi.yi), na.rm=TRUE)

#去除最后一个数字 没用
di.1.yue <- head(di.1.yue,-1)
#第二个月
di.2.yue<-DF$`0`/2
#第三个月
#  1997年3月等于2/3* 97q1 +1/3 * 97q
#不需要q1的2/3
new.one<-third[-1]
new.two<-head(two,-1)
di.3.yue<-rowMeans(cbind(new.one,new.two),na.rm=TRUE)
di.3.yue<-append(di.3.yue,0,after = 98)
#交叉合并
ab <- as.vector(matrix(c(di.1.yue, di.2.yue,di.3.yue), nrow = 3, byrow = TRUE))
ab
#
smooth.data<-data.frame(matrix(nrow = 298,ncol = 2))
#date
smooth.data$date <-seq(from = as.Date("1997-01-01"), to = as.Date("2021-10-01"),
           by = "month")#生成日期
smooth.data$Total_expenditure<-c(ab,0)
fdf<-smooth.data[,-c(1:2)]
#write.csv(fdf,"smooth data for total expenditure.csv",row.names = FALSE)
fdf<-fdf[-c(297:298),]
```
# Process
According to your suggestion, I made quarterly into smoothed monthly data. The idea is I give Jan, April, July and Oct 1/3 weight of the previous quarter and 2/3 current quarter, sum up and divided by 2. 
Feb, May, August, Nov keep their quarter figures and divide by 2.
March, June, Sept and Dec have given 1/3 of the previous quarter and 2/3 current quarter, sum up and divided by 2. 


```{r , echo=FALSE, fig.cap="Total expenditure", fig.topcaption=TRUE, message=FALSE, warning=FALSE,results='asis'}
p<-ggplot(data=fdf, aes(x=date))+
 geom_line(aes(y =Total_expenditure, color="Total_expenditure")) +
labs(x="Time",y="millions pounds")
p
```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tseries)
df.ts<-ts(fdf$Total_expenditure,frequency = 12,start = c(1997,1))
adf.test(df.ts)
```
# Augmented Dickey-Fuller Test

One way to test whether a time series is stationary is to perform an augmented Dickey-Fuller test, which uses the following null and alternative hypotheses:

H0: The time series is non-stationary. In other words, it has some time-dependent structure and does not have constant variance over time.

HA: The time series is stationary.

P-value: 0.1469

Since the p-value is  0.1469 not less than .05, we fail to reject the null hypothesis.

This means the time series is non-stationary. In other words, it has some time-dependent structure and does not have constant variance over time.

# Growh rate

Since total expenditure monthly data is not stationary, I try to convert to a percentage growth rate.

```{r growth rate, , include=FALSE}
library(dplyr)
growth_rate <- function(x)(x/lag(x)-1)*100 
fdf$growth_rate <- growth_rate(fdf$Total_expenditure) 
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(tseries)
fdf<-fdf[-(1:2),]
df.ts<-ts(fdf$growth_rate,frequency = 12,start = c(1997,1))
adf.test(df.ts)
```

We examine the growth rate stationary by applying the ADF test. The p-value is 0.01; we reject the null hypothesis. This means the time series is stationary now. 

After we perform an augmented Dickey-Fuller test on the data, we can create a quick plot to visualize the data: There was a very clear fluctuation between March and August 2020.

```{r , echo=FALSE, fig.cap="Growth rate", fig.topcaption=TRUE, message=FALSE, warning=FALSE,results='asis'}
q<-ggplot(data=fdf, aes(x=date))+
 geom_line(aes(y =growth_rate, color="growth rate")) +
labs(x="Time",y="Growth rate percent change")
q
```

\newpage

# Questions:

Now we have a stationary monthly demand variable, but I am not sure how I can do it for the general CPI model and the 12 COCOP divisions.
The following formula is how we model inflation in chapter 1. My plans are: : replace CPI in the right hand to 12 lags demand variables and keep rest dummies variables. I would be appreciated it if you could provide more suggestions.
$$
\begin{aligned}
	CPI_t=&CPI+\,\,\mathrm{Trend}_t+\beta _1Q_1+\beta _2Q_3+\beta _3Q_4\\
	&+\beta _4D_{\mathrm{recesion}}+\beta _5D_{VAT_1}+\beta _6D_{VAT_2}+\beta _7D_{VAT_3}\\
	+\sum_{i=1}^4{\lambda _i}CPI_{t-i}+\sigma _t\\
\end{aligned}
$$

```{r eval=FALSE, include=FALSE}
#write.csv(fdf,"monthly consumption data and growth rate.csv",row.names = FALSE)
```

