---
title: "latex test"
author: "Yiyi"
date: "`r Sys.Date()`"
output:
  pdf_document:
          toc: yes
  header-includes:
  - \usepackage{placeins}
  - \usepackage{multirow}
  - \usepackage{multicolumn}
  - \usepackage{caption}
  - \usepackage[absolute,overlay]{textpos}
  - \usepackage{float}
  - \usepackage{graphicx}
  - \usepackage{booktabs}
  html_document:
    toc: yes
    df_print: paged
  word_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
 rm(list = ls())
Sys.setlocale("LC_TIME", "English")
```

```{r Library, include=FALSE}
#Packages
library(readxl)
library(data.table)
library(lubridate)#extract cpi time to newdata(furniture48)
library(dplyr) 
library(tidyverse) 
library(broom)
library(stargazer)
library(knitr)
library(officer)
library(flextable)
library(magrittr)
library(dplyr)
library(moments)
library(Inflation)
library(ggplot2)
library(zoo)
library(xts)
library(hydroTSM)
library(openair)
library(tibble)
library(miscTools)
library(priceR)
library(Metrics)
```


\begin{table}[]
\centering
\caption{Forecasting future inflation}
\label{tab:my-table}
\begin{tabular}{|c|cll|}
\hline
H                       & \multicolumn{3}{c|}{Excluding Food and Energy}                              \\ \hline
                        & \multicolumn{1}{c|}{a} & \multicolumn{1}{c|}{b} & \multicolumn{1}{c|}{RMSE} \\ \hline
\multicolumn{1}{|l|}{6} & \multicolumn{1}{l|}{}  & \multicolumn{1}{l|}{}  &                           \\ \hline
\multicolumn{1}{|l|}{9} & \multicolumn{1}{l|}{}  & \multicolumn{1}{l|}{}  &                           \\ \hline
12 & \multicolumn{1}{c|}{0.229} & \multicolumn{1}{c|}{0.817} & \multicolumn{1}{c|}{1.155487} \\ \hline
\end{tabular}
\end{table}

