---
title: "quarterly summary table"
author: "Yiyi"
date: "`r Sys.Date()`"
output:
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
---
## Packages
```{r Library, include=FALSE}
library(readxl)
library(data.table)
library(lubridate)#extract cpi time to newdata(furniture48)
library(dplyr) 
library(tidyverse) 
library(broom)
library(stargazer)
library(knitr)
library(officer)
library(flextable)
library(magrittr)
library(dplyr)
library(largeList)
```
# Table 3  Summary table before stepwise (Quarterly data)

**修正summary table 在代码体现最大的变化应该是在run完regression的时候, 再把出去division and groupd的class 汇总在一起 生成新的sig.class, 在对季度数据应用的时候应当也是如此**

```{r}
rm(list = ls())
Sys.setlocale("LC_TIME", "English")
```

```{r}
cpi <- read_excel("correct quarter cpi.xlsx")#108
cols.num <- c(colnames(cpi))#cols.列名
cpi[cols.num] <- sapply(cpi[cols.num],as.numeric)#把所有数据转成数字类型?

cpi <- as.data.table(cpi)
colnames(cpi) = gsub("&", "and", colnames(cpi))#把列名里&换成 and
COPY<-copy(cpi)
tracemem(COPY)==tracemem(cpi)
Data_A = as.data.table (cpi)

Varnames <- copy(names(Data_A))#
Data_A[, (names(Data_A)) := lapply(.SD, as.numeric)][,
                                                     rn := .I]
melted <- melt(Data_A, id.vars="rn")[,
                                     (paste0("lag_", 0:4)) := shift(value, 0:4, type="lag"),
                                     by=variable][, 
                                                  value:=NULL][]
res <- dcast.data.table(melt(melted, id.vars=c("rn", "variable"), variable.name="lag"),
                        rn ~ variable + lag, sum)
res[, ncol(res), with=FALSE]
cpi <- cpi[, unlist(lapply(.SD, shift, n = 0:4), recursive = FALSE)]#lags generation
# quarterly  Dummies ---------------------------------------------------------


cpi$time <- seq.Date(from = as.Date("1992/01/01",format = "%Y/%m/%d"), by = "quarter", length.out = 112)
cpi$time <- format(cpi$time, format = "%b")

cpi <- fastDummies::dummy_cols(cpi, select_columns = "time", remove_most_frequent_dummy = TRUE,
)

cpi$time1 <- seq.Date(from = as.Date("1992/01/01",format = "%Y/%m/%d"), by = "quarter", length.out = 112)
# Trend,vat, recession ----------------------------------------------------

newdata<-copy(cpi)

newdata<-newdata[newdata$'time1' >= as.Date("1993-01-01")]
Trend <- seq_along(newdata$time1)

VAT1 <- as.numeric(newdata$`time1` == "2008-10-01")
VAT2 <- as.numeric(newdata$`time1` == "2010-01-01")
VAT3 <- as.numeric(newdata$`time1` == "2011-01-01")
Recession <- as.numeric(newdata$`time1` >= "2008-04-01" & newdata$`time1`<= "2009-06-01")
# Lag ---------------------------------------------------------------------

lag1 <- newdata %>% 
  select(matches("(2)$"))
lag2 <- newdata %>% 
  select(matches("(3)$"))
lag3 <- newdata %>% 
  select(matches("(4)$"))
lag4 <- newdata %>% 
  select(matches("(5)$"))

# quarterly DUMMIES --------------------------------------------------------


quarter1 <- as.numeric(newdata$time_Jan)
quarter3 <- as.numeric(newdata$time_Jul)
quarter4 <- as.numeric(newdata$time_Oct)

COPY <- as.data.frame(COPY)
lag1 <- as.data.frame(lag1)
lag2 <- as.data.frame(lag2)
lag3 <- as.data.frame(lag3)
lag4 <- as.data.frame(lag4)

# CPI-LAGS ----------------------------------------------------------------


CPI_lag1 <- (newdata$"CPI ALL ITEMS2")
CPI_lag2 <- (newdata$"CPI ALL ITEMS3")
CPI_lag3 <- (newdata$"CPI ALL ITEMS4")
CPI_lag4 <- (newdata$"CPI ALL ITEMS5")

```
```{r}
# Copy删除前四行? --------------------------------------------------

COPY<-COPY[-1:-4,]
```
## Regression
```{r}
regression <- lapply(1:122, function(x) lm(COPY[,x] ~ lag1[,x]+lag2[,x]+lag3[,x]+lag4[,x]+CPI_lag1+CPI_lag2+CPI_lag3+CPI_lag4+ quarter1+quarter3+quarter4+VAT1+VAT2+VAT3+Recession+Trend)
)
for (i in 1:122) {
  names(regression[[i]]$coefficients)<-c('Constant','lag1','lag2',"lag3","lag4",
                                         "CPI_lag1","CPI_lag2","CPI_lag3","CPI_lag4",
                                         "quarter1","quarter3","quarter4",
                                         "VAT1","VAT2","VAT3","Recession","Trend")
}
```
## **85部门版本合集生成**
```{r}
sig.class<-c(regression[4:12],regression[14:15],#1,
             regression[18:21],#2
             regression[24:27],#3
             regression[29],regression[31:32],regression[34:35],regression[37:40],#4
             regression[43:45],regression[47:50],regression[52:53],#5
             regression[56:57],regression[59:61],#6
             regression[64:66],regression[68:71],regression[73:76],#7
             regression[78:79],#8
             regression[82:86],regression[88],regression[90:93],regression[95:96],regression[98:100],regression[101],#9
             regression[102],#10
             regression[105:107],#11
             regression[110:111],regression[113:115],regression[117:119],regression[121:122])#12
```


可以重复了
下面是重复yearly 部分
```{r}

percent <- function(x, digits = 2, format = "f", ...) {
  paste0(formatC(100 * x, format = format, digits = digits, ...), "%")
}
# Weight ------------------------------------------------------------------
weight<- list(0.109,	0.042,	0.063,	0.115,	0.067,	0.022,	0.152,	0.023,	0.152,	0.019,	0.137,	0.099
              
)
Reduce("+",weight)
```
用lapply sig.class 这个list 化成长数据框类型.(多行,5列:term,estimate,std,statitc, pvalue)
```{r}

tidy_mods <- lapply(sig.class, tidy)

for (i in 1:length(tidy_mods)) 
  tidy_mods[[i]]$mod <- names(tidy_mods[i])
a <- do.call(rbind.data.frame, tidy_mods)

```



## 各部门开始结束位置df
```{r}
class.poi<-data.frame(matrix(nrow = 13,ncol = 2),row.names = 1:13)
names(class.poi)<-c("start","end")
poi<-c(1,11,4,4,9,9,5,11,2,16,1,3,10)
class.poi[,1]<-c(cumsum(poi))#每个部门开始的位置
class.poi[,2]<-c((class.poi[,1]-1)[-1],"na")#结束的位置
class.poi<-head(class.poi,-1)#删除最后一行

```
**60属于第9部门**
**根据 intercept 开始的位置, 和trend结束位置 划分df**

```{r}
start<-class.poi[,1]
start[1+1]-1
end<-as.numeric(class.poi[,2])
for (i in 1:12) {
  assign(paste0("a",i),
         a[
           (which(a$term=="Constant")[start[i]])
           :
             (which(a$term=="Trend")[end[i]])
           ,]
         )
}
```

把各部门的长度存储在class_length
```{r}
class_length<-data.frame(matrix(nrow = 12,ncol = 1))
for(i in 1:12){
  class_length[i,1]<-length(which(get(paste0("a",i))$term=="Trend"))
}
```

### a_lag.0.01
```{r}

a_lag.0.01<-data.frame( row.names =  paste0("lag",1:4),
                   matrix(nrow=4, ncol=12, ) ) 

colnames(a_lag.0.01)<-c(paste0("a",1:12))
i<-1#i=a,j=lag
while (i <=12) {
  for (j in 1:4) {
 a_lag.0.01 [j,i]  <-
  length( which((get(paste0("a",i)))$term==paste0("lag",j)&(get(paste0("a",i)))$p.value<0.01)
  )/length(which(get(paste0("a",i))$term=="Trend"))*weight[[i]]
  }
  i<-i+1
}
```
### a_lag.0.05
```{r}
a_lag.0.05<-data.frame( row.names =  paste0("lag",1:4),
                   matrix(nrow=4, ncol=12, ) ) 

colnames(a_lag.0.05)<-c(paste0("a",1:12))
i<-1#i=a,j=lag
while (i <=12) {
  for (j in 1:4) {
 a_lag.0.05 [j,i]  <-
  length( which((get(paste0("a",i)))$term==paste0("lag",j)&(get(paste0("a",i)))$p.value<0.05)
  )/length(which(get(paste0("a",i))$term=="Trend"))*weight[[i]]
  }
  i<-i+1
}
```
### a_cpi.0.01

```{r}
a_cpi.0.01<-data.frame( row.names =  paste0("CPI_lag",1:4),
                   matrix(nrow=4, ncol=12, ) ) 

colnames(a_cpi.0.01)<-c(paste0("a",1:12))
i<-1#i=a,j=lag
while (i <=12) {
  for (j in 1:4) {
 a_cpi.0.01 [j,i]  <-
  length( which((get(paste0("a",i)))$term==paste0("CPI_lag",j)&(get(paste0("a",i)))$p.value<0.01)
  )/length(which(get(paste0("a",i))$term=="Trend"))*weight[[i]]
  }
  i<-i+1
}
```
### a_cpi.0.05
```{r}
a_cpi.0.05<-data.frame( row.names =  paste0("CPI_lag",1:4),
                   matrix(nrow=4, ncol=12, ) ) 

colnames(a_cpi.0.05)<-c(paste0("a",1:12))
i<-1#i=a,j=lag
while (i <=12) {
  for (j in 1:4) {
 a_cpi.0.05 [j,i]  <-
  length( which((get(paste0("a",i)))$term==paste0("CPI_lag",j)&(get(paste0("a",i)))$p.value<0.05)
  )/length(which(get(paste0("a",i))$term=="Trend"))*weight[[i]]
  }
  i<-i+1
}
```

# table3写入,这次要生成8*4的dataframe
```{r}
table3Quarterlydata<-data.frame( matrix(nrow=8, ncol=4, )   )
colnames(table3Quarterlydata)<-c("p<0.01","p<0.05","p<0.01(Weight)","p<0.05(Weight)")
rownames(table3Quarterlydata)<-c(paste0("CPI_lag",1:4),paste0("lag",1:4))
```
写入结果

```{r}

for (i in 1:4) {#前两列
  table3Quarterlydata[i,1]<-percent((length( which(a$term==paste0("CPI_lag",i)&(a$p.value<0.01))))/85)
   table3Quarterlydata[i+4,1]<-percent((length( which(a$term==paste0("lag",i)&(a$p.value<0.01))))/85)
   table3Quarterlydata[i,2]<-percent((length( which (a$term==paste0("CPI_lag",i)&(a$p.value<0.05))))/85)
      table3Quarterlydata[i+4,2]<-percent((length( which(a$term==paste0("lag",i)&(a$p.value<0.05))))/85)
      #后两列
    table3Quarterlydata[i,3]<-percent(sum(a_cpi.0.01[paste0("CPI_lag",i),])      )
    table3Quarterlydata[i+4,3]<-percent(sum(a_lag.0.01[paste0("lag",i),]))
    table3Quarterlydata[i,4]<-percent(sum(a_cpi.0.05[paste0("CPI_lag",i),]))
    table3Quarterlydata[i+4,4]<-percent(sum(a_lag.0.05[paste0("lag",i),]))
    
}

```

flextable 写入word
```{r}

ft1<-flextable(table3Quarterlydata %>% rownames_to_column("column name"))




save_as_docx("Summary table before stepwise (Quarterly data)" = ft1, path = "F:/R workspace/Modelling-UK-inflation-quarterly-/table3.docx")




```

***

# quarterly stepwise

## stepwise function
```{r include=FALSE}
# function ----------------------------------------------------------------


# Automated model selection
# Author      : Joris Meys
# version     : 0.2
# date        : 12/01/09

#CHANGE LOG
# 0.2   : check for empty scopevar vector

# #CHANGE LOG -------------------------------------------------------------



# Function has.interaction checks whether x is part of a term in terms
# terms is a vector with names of terms from a model
has.interaction <- function(x,terms){
  out <- sapply(terms,function(i){
    sum(1-(strsplit(x,":")[[1]] %in% strsplit(i,":")[[1]]))==0
  })
  return(sum(out)>0)
}

# Function Model.select
# model is the lm object of the full model
# keep is a list of model terms to keep in the model at all times
# sig gives the significance for removal of a variable. Can be 0.1 too (see SPSS)
# verbose=T gives the F-tests, dropped var and resulting model after 
model.select <- function(model,keep,sig=0.05,verbose=F){
  counter=1
  # check input
  if(!is(model,"lm")) stop(paste(deparse(substitute(model)),"is not an lm object\n"))
  # calculate scope for drop1 function
  terms <- attr(model$terms,"term.labels")
  if(missing(keep)){ # set scopevars to all terms
    scopevars <- terms
  } else{            # select the scopevars if keep is used
    index <- match(keep,terms)
    # check if all is specified correctly
    if(sum(is.na(index))>0){
      novar <- keep[is.na(index)]
      warning(paste(
        c(novar,"cannot be found in the model",
          "\nThese terms are ignored in the model selection."),
        collapse=" "))
      index <- as.vector(na.omit(index))
    }
    scopevars <- terms[-index]
  }
  
  # Backward model selection : 
  
  while(T){
    # extract the test statistics from drop.
    test <- drop1(model, scope=scopevars,test="F")
    
    if(verbose){
      cat("-------------STEP ",counter,"-------------\n",
          "The drop statistics : \n")
      print(test)
    }
    
    pval <- test[,dim(test)[2]]
    
    names(pval) <- rownames(test)
    pval <- sort(pval,decreasing=T)
    
    if(sum(is.na(pval))>0) stop(paste("Model",
                                      deparse(substitute(model)),"is invalid. Check if all coefficients are estimated."))
    
    # check if all significant
    if(pval[1]<sig) break # stops the loop if all remaining vars are sign.
    
    # select var to drop
    i=1
    while(T){
      dropvar <- names(pval)[i]
      check.terms <- terms[-match(dropvar,terms)]
      x <- has.interaction(dropvar,check.terms)
      if(x){i=i+1;next} else {break}              
    } # end while(T) drop var
    
    if(pval[i]<sig) break # stops the loop if var to remove is significant
    
    if(verbose){
      cat("\n--------\nTerm dropped in step",counter,":",dropvar,"\n--------\n\n")              
    }
    
    #update terms, scopevars and model
    scopevars <- scopevars[-match(dropvar,scopevars)]
    terms <- terms[-match(dropvar,terms)]
    
    formul <- as.formula(paste(".~.-",dropvar))
    model <- update(model,formul)
    
    if(length(scopevars)==0) {
      warning("All variables are thrown out of the model.\n",
              "No model could be specified.")
      return()
    }
    counter=counter+1
  } # end while(T) main loop
  return(model)
}

```

```{r }
slr.total <- list()
keep.dummies <- c("quarter1","quarter3","quarter4",
                  "VAT1","VAT2","VAT3","Recession","Trend")
for (i in 1:length(sig.class)) {
  slr.total[[i]] <- model.select(sig.class[[i]], keep = keep.dummies, sig = 0.05, verbose = F)
}


```

## 寻找消失的部门的位置

slr.total所有变量都不显著的部门

```{r}
names(slr.total) <- 1:length(slr.total)
class_with_no_significant <- slr.total[which(sapply(slr.total, is.null))]
length(class_with_no_significant)
```

```{r}
#去除不显著的
slr.total[sapply(slr.total, is.null)] <- NULL
#替换名称
search_for_these <- c("lag1[, x]","lag2[, x]","lag3[, x]","lag4[, x]","lag5[, x]","lag6[, x]","lag7[, x]","lag8[, x]","lag9[, x]","lag10[, x]","lag11[, x]","lag12[, x]")
 replace_with_these <- c("lag1","lag2","lag3","lag4","lag5","lag6","lag7","lag8","lag9","lag10","lag11","lag12")
 found<-list()
for (i in 1:length(slr.total)) {
  found[[i]] <- match(names(slr.total[[i]]$coefficients), search_for_these, nomatch = 0)
  names(slr.total[[i]]$coefficients)[names(slr.total[[i]]$coefficients) %in% search_for_these] <- replace_with_these[found[[i]]]
}
```

```{r}
#化成长数据类型
 tidy_stepwsie <- lapply(slr.total, tidy)
  stepwsie_a<- do.call(rbind.data.frame, tidy_stepwsie)
  length(which(stepwsie_a$term=="VAT1"))

```

## 各部门开始结束位置df
```{r}
miss.class<-c(1,0,0,2,0,1,3,1,2,0,0,2)
sum(miss.class)
class_length_stepwise_quarterly<-data.frame(matrix(nrow = 12,ncol = 1))
class_length_stepwise_quarterly[,1]<-c(class_length[,1]-miss.class)
```

```{r}
class.poi<-data.frame(matrix(nrow = 13,ncol = 2),row.names = 1:13)
names(class.poi)<-c("start","end")
poi<-c(1,class_length_stepwise_quarterly[,1])
class.poi[,1]<-c(cumsum(poi))#每个部门开始的位置
class.poi[,2]<-c((class.poi[,1]-1)[-1],"na")#结束的位置
class.poi<-head(class.poi,-1)#删除最后一行
write.csv(class.poi,"F:/R workspace/Modelling-UK-inflation-quarterly-/class-poisition_stepwise_quarterly.csv")




```

**根据 intercept 开始的位置, 和trend结束位置 划分df**
```{r}
start<-class.poi[,1]

end<-as.numeric(class.poi[,2])
for (i in 1:12) {
  assign(paste0("stepwsie_a",i),
         stepwsie_a[
           (which(stepwsie_a$term=="(Intercept)")[start[i]])
           :
             (which(stepwsie_a$term=="Trend")[end[i]])
           ,]
         )
}
length(which(stepwsie_a12$term=="Trend"))
```
```{r}
class_length_73<-data.frame(matrix(nrow = 12,ncol = 1))
for(i in 1:12){
  class_length_73[i,1]<-length(which(get(paste0("stepwsie_a",i))$term=="Trend"))
}
```

## 创建	Table 4 Stepwise Summary Table 存储结果 是8*4.
```{r}
stepwise_table_quarterly<-data.frame( matrix(nrow=8, ncol=4, )   )
colnames(stepwise_table_quarterly)<-c("p<0.01","p<0.05","p<0.01(Weight)","p<0.05(Weight)")
rownames(stepwise_table_quarterly)<-c(paste0("CPI_lag",1:4),paste0("lag",1:4))
```

### stepwise_lag_0.01_quarterly
```{r}

stepwise_lag_0.01_quarterly<-data.frame( row.names =  paste0("lag",1:4),
                   matrix(nrow=4, ncol=12, ) ) 

colnames(stepwise_lag_0.01_quarterly)<-c(paste0("a",1:12))
i<-1#i=a,j=lag
while (i <=12) {
  for (j in 1:4) {
 stepwise_lag_0.01_quarterly [j,i]  <-
  length( which((get(paste0("stepwsie_a",i)))$term==paste0("lag",j)&(get(paste0("stepwsie_a",i)))$p.value<0.01)
  )/length(which(get(paste0("stepwsie_a",i))$term=="Trend"))*weight[[i]]
  }
  i<-i+1
}

```
### stepwise_lag_0.05_quarterly
```{r}

stepwise_lag_0.05_quarterly<-data.frame( row.names =  paste0("lag",1:4),
                   matrix(nrow=4, ncol=12, ) ) 

colnames(stepwise_lag_0.05_quarterly)<-c(paste0("a",1:12))
i<-1#i=a,j=lag
while (i <=12) {
  for (j in 1:4) {
 stepwise_lag_0.05_quarterly [j,i]  <-
  length( which((get(paste0("stepwsie_a",i)))$term==paste0("lag",j)&(get(paste0("stepwsie_a",i)))$p.value<0.05)
  )/length(which(get(paste0("stepwsie_a",i))$term=="Trend"))*weight[[i]]
  }
  i<-i+1
}
```

### stepwise_cpi_0.01_quarterly
```{r}

stepwise_cpi_0.01_quarterly<-data.frame( row.names =  paste0("CPI_lag",1:4),
                   matrix(nrow=4, ncol=12, ) ) 

colnames(stepwise_cpi_0.01_quarterly)<-c(paste0("a",1:12))
i<-1#i=a,j=lag
while (i <=12) {
  for (j in 1:4) {
 stepwise_cpi_0.01_quarterly [j,i]  <-
  length( which((get(paste0("stepwsie_a",i)))$term==paste0("CPI_lag",j)&(get(paste0("stepwsie_a",i)))$p.value<0.01)
  )/length(which(get(paste0("stepwsie_a",i))$term=="Trend"))*weight[[i]]
  }
  i<-i+1
}
```

### stepwise_cpi_0.05_quarterly
```{r}

stepwise_cpi_0.05_quarterly<-data.frame( row.names =  paste0("CPI_lag",1:4),
                   matrix(nrow=4, ncol=12, ) ) 

colnames(stepwise_cpi_0.05_quarterly)<-c(paste0("a",1:12))
i<-1#i=a,j=lag
while (i <=12) {
  for (j in 1:4) {
 stepwise_cpi_0.05_quarterly [j,i]  <-
  length( which((get(paste0("stepwsie_a",i)))$term==paste0("CPI_lag",j)&(get(paste0("stepwsie_a",i)))$p.value<0.05)
  )/length(which(get(paste0("stepwsie_a",i))$term=="Trend"))*weight[[i]]
  }
  i<-i+1
}
```

# 写入table4
```{r}
for (i in 1:4) {#前两列
  stepwise_table_quarterly[i,1]<-percent((length( which(stepwsie_a$term==paste0("CPI_lag",i)&(stepwsie_a$p.value<0.01))))/85)
   stepwise_table_quarterly[i+4,1]<-percent((length( which(stepwsie_a$term==paste0("lag",i)&(stepwsie_a$p.value<0.01))))/85)
   stepwise_table_quarterly[i,2]<-percent((length( which(stepwsie_a$term==paste0("CPI_lag",i)&(stepwsie_a$p.value<0.05))))/85)
      stepwise_table_quarterly[i+4,2]<-percent((length( which(stepwsie_a$term==paste0("lag",i)&(stepwsie_a$p.value<0.05))))/85)
      #后两列
    stepwise_table_quarterly[i,3]<-percent(sum(stepwise_cpi_0.01_quarterly[paste0("CPI_lag",i),])      )
    stepwise_table_quarterly[i+4,3]<-percent(sum(stepwise_lag_0.01_quarterly[paste0("lag",i),]))
    stepwise_table_quarterly[i,4]<-percent(sum(stepwise_cpi_0.05_quarterly[paste0("CPI_lag",i),]))
    stepwise_table_quarterly[i+4,4]<-percent(sum(stepwise_lag_0.05_quarterly[paste0("lag",i),]))
    
}
```
## flextable 写入word
```{r}



ft1<-flextable(stepwise_table_quarterly %>% rownames_to_column("column name"))




save_as_docx("	Table 4 Stepwise Summary Table (Quarterly data)" = ft1, path = "F:/R workspace/Modelling-UK-inflation-quarterly-/table4.docx")




```
