---
title: "Trimmed mean ITEM"
author: "Yiyi"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: yes
    toc_depth: '3'
  html_document:
    highlight: tango
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 3
  pdf_document:
    toc: yes
    toc_depth: '3'
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
 rm(list = ls())
Sys.setlocale("LC_TIME", "English")
```

## 

```{r Library, include=FALSE}
#Packages
library(readxl)
library(data.table)
library(lubridate)#extract cpi time to newdata(furniture48)
library(dplyr) 
library(tidyverse) 
library(broom)
library(stargazer)
library(knitr)
library(officer)
library(flextable)
library(magrittr)
library(dplyr)
library(moments)
library(Inflation)
library(ggplot2)
library(zoo)
library(xts)
library(hydroTSM)
library(openair)
library(tibble)
library(miscTools)
library(priceR)
library(Metrics)

```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
Sys.setlocale("LC_TIME","English")
```

# DATA

For this time Trimmed means I did based on items level. The data set
started from 2.2006 to 4.2021 and covers 1144 items.

The trimmed means used here are calculated on a Year-on-year basis, but
I the paper "MEASURING AND ASSESSING UNDERLYING INFLATION" you suggested
are calculated on a month-on-month basis. Year-on-year or three-month
inflation rates are then obtained by compounding monthly trimmed mean
inflation rates.

# Item index

```{r include=FALSE}
#读取数据
item_cpi<-read_excel("item_indices_complete.xlsx","Sheet2")
#合并第一行和列名
colnames(item_cpi)=paste(colnames(item_cpi),item_cpi[1,])
#第一行和第二列没啥东西 都删了
item_cpi<-item_cpi[-1,-2]

#各列属性目前是character
#sapply(item_cpi,class)
#转化为numerical
#除了前第一列以外别的列转化为numerical
item_cpi[, 2:ncol(item_cpi)] <- sapply(item_cpi[,2:ncol(item_cpi)], as.numeric)
#

#把cpi指数换算成年度inflation， 第一列是时间
#这里到底用年度还是月度？
df<-as.data.table(item_cpi)[, lapply(.SD, function(x)x/shift(x,12,type = "lag")-1), .SDcols = 2:ncol(item_cpi)]
df<-df*100
#添加日期
date = seq(from = as.Date("2005-02-01"), to = as.Date("2021-04-01"),
           by = "month")#生成日期
#合并日期
zxc<-add_column(df,date,.before = 1)
#只保留2006年之后的，因为数据从05年开始，年度inflation的话inflation 没有之前一年的数据相比了。
qwe<-zxc[zxc$date>="2006-02-01",]

write.csv(qwe,file = "ITEM Index 2016.csv")
qwe<-qwe[,-1]
#把na换成0
qwe<-as.data.frame(qwe)
qwe[is.na(qwe)]<-0
item_index_final<-qwe
#转化成从2005年开始的年度ts 数据类型
ix.ts<-ts(qwe,start = c(2006,2),frequency = 12 )
```

# ITEM Weight

```{r include=FALSE}
item_weight<-read_excel("item_indices_complete.xlsx","Sheet3")
#合并第一行和列名
colnames(item_weight)=paste(colnames(item_weight),item_weight[1,])
#第一行和第二列没啥东西 都删了
item_weight<-item_weight[-1,-2]
#除了前第一列以外别的列转化为numerical
item_weight[, 2:ncol(item_weight)] <- sapply(item_weight[,2:ncol(item_weight)], as.numeric)
#我看看每个月（行的和）weight 和是多少
#从来没有等于过1000.
#有nan值似乎无法计算
item_weight<-as.data.frame(item_weight)
item_weight[is.na(item_weight)]<-0
#合并日期
item_weight_final<-add_column(item_weight,date,.before = 1)
#只保留2006年之后的，因为数据从05年开始，年度inflation的话inflation 没有之前一年的数据相比了。
item_weight_final<-item_weight_final[item_weight_final$date>="2006-02-01",]
#
write.csv(item_weight_final,file = "weight Index 2016.csv")
#删除时间
item_weight_final<-item_weight_final[,-(1:2)]
#全都是900多。就没有个1000的
#rowSums(item_weight_final[,2:ncol(item_weight_final)])
#现在都是千分比，需不需要换成百分比？
##巴西的例子 权重是百分比。
#全部/10和就是100了
item_weight_final<-item_weight_final/10


#rowSums(item_weight_final[,2:ncol(item_weight_final)])
w.ts<-ts(item_weight_final,start = c(2006,2),frequency = 12)

```

#Three thresholds are used: 15, 20 and 25%.

```{r Trimmed mean, include=FALSE}
#run core inflation
cf<-INFL.core_tm(subits.var = ix.ts,weights = w.ts)
nt<-ts(cf$core,start = c(2006,2),frequency = 12)
```

#25%

```{r include=FALSE}
cf25<-INFL.core_tm(subits.var = ix.ts,weights = w.ts, inf = 25, sup = 25)
nt25<-ts(cf25$core,start = c(2006,2),frequency = 12)
```

#15%

```{r include=FALSE}
cf15<-INFL.core_tm(subits.var = ix.ts,weights = w.ts, inf = 15, sup = 15)
nt15<-ts(cf15$core,start = c(2006,2),frequency = 12)
```

```{r include=FALSE}
#10% 10以下开始不执行了
#cf10<-INFL.core_tm(subits.var = ix.ts,weights = w.ts, inf = 10, sup = 10)
#nt10<-ts(cf10$core,start = c(2006,2),frequency = 12)
```

# Plot

```{r include=FALSE}
#cpi是数据是05到19的，cf数据是06到21的
#我他妈重新下一个cpi数据把 cpi数据是2.06-4.21
CPI_ANNUAL_06_21<-read_excel("2.06-4.21 cpi ANNUAL RATE.xlsx")
trimmed_CPI<-add_column(CPI_ANNUAL_06_21,cf25$core,cf$core,cf15$core,.after = 2)
trimmed_CPI<-trimmed_CPI[,-1]
#时间
date06 = seq(from = as.Date("2006-02-01"), to = as.Date("2021-04-01"),
           by = "month")#生成日期
#插入日期
trimmed_CPI<-add_column(trimmed_CPI,date06,.before = 1)
#命名
colnames(trimmed_CPI)<-c("date","CPIInflation","Trimmed25percent","Trimmed20percent","Trimmed15percent")



write.csv(trimmed_CPI,"trimmed mean 06-21.csv",row.names = FALSE)
#读取cpi inflation数据

#ggplot
nt<-ts(trimmed_CPI$date,start = c(2006,2),frequency = 12 )
p<-ggplot(data=trimmed_CPI, aes(x=time(nt)))+
 geom_line(aes(y = CPIInflation, color="CPI Inflation")) +
   geom_line(aes(y = Trimmed25percent, color="25 Trimming percentage")) +
     geom_line(aes(y = Trimmed20percent, color="20 Trimming percentage")) +
       geom_line(aes(y = Trimmed15percent, color="15 Trimming percentage")) +
labs(x="Time",y="Inflation")
  
```

```{r  echo=FALSE, fig.cap = "68 classes CPI and core inflation excluding food and energy.",fig.topcaption=TRUE}
p + theme(legend.title = element_blank()) 
```
