---
title: "R Notebook"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
 rm(list = ls())
Sys.setlocale("LC_TIME", "English")
```

```{r Library, include=FALSE}
#Packages
library(readxl)
library(data.table)
library(lubridate)#extract cpi time to newdata(furniture48)
library(dplyr) 
library(tidyverse) 
library(broom)
library(stargazer)
library(knitr)
library(officer)
library(flextable)
library(magrittr)
library(dplyr)
library(moments)
library(Inflation)
library(ggplot2)
library(zoo)
library(xts)
library(hydroTSM)
library(openair)
library(tibble)
library(miscTools)
library(priceR)
library(Metrics)

```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
Sys.setlocale("LC_TIME","English")
```

# Criteria for evaluation : forecasting future inflation

The ability of the core inflation indicator to predict future headline inflation can be quantified by the following regression equation.

```{r include=FALSE}
#想在r markdown里输入latex公式居中 首先需要首位$$\begin{} \end{}$$
#这个 公式模型 我自己用ols也能做啊？
#就做一个df，有三列数据，第一列x_t+12,第二列x_t,第三列core
#日期的问题
#
```


Here, x represents the headline inflation rate and core x represents some core inflation indicator, both year-on-year data. Parameter h is 12 (month) ahead in this case. For sufficiently large H, the core deviation, $\left(x_{t}^{\text {core }}-x_{t}\right)$, should be inversely related to subsequent changes in inflation, $x_{t+h}-x_{t}$. Moreover, in order for the candidate to satisfy equation (1), the coefficients in the regression, should satisfy $\alpha=0$ and $\beta_H = -1$.


\begin{equation}
x_{t+h}-x_{t}=\alpha+\beta\left(x_{t}^{\text {core }}-x_{t}\right)+\varepsilon_{t}
\end{equation}